A thesis draft

### 2018-11-16 res/sections/25-Tests.tex
Add graphs and jitter table

\subsection{RTT measurement}
Regarding the delivery performance, a metric to take in account is the \emph{round trip time}(RTT), that is the time interval between the instant in whic a packet is sent and the response is received. To test it there was developed a script that sends a packet and waits for the corrispondant response, recording the instants (expressed as \emph{epoch}) of send and receive. The sake of thi test is to compare the RTT measured without any SFC (only sending the packet to the receiver waiting for the response) and making packets pass through different length SFCs, in particular with 1, 2, 3, 4, 5, and 10 hops. Packets traverse the SFC on both sides and the results are collected after 100 tests and the SF only prints the packet received and the total number of packets that have passed throught it.

@@

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.35]{meanrtt}
  \caption{Mean RTT calculate using SFCs with different lengths}
  \label{chap:tests:sec:rtt:img:meanstt}
\end{figure}

The results are better represented in Figure~\ref{chap:tests:sec:rtt:img:meanstt}. In that graph we can easier see the difference among the chains with different lengths and the trasmission that does not use any SFC. Looking at the bars representing the SFC composed by 1, 2, 3, 4 and 5 links we can see a pretty linear increase of the RTT. This trend strongly depends on the nature of the SF involved in the SFC.

>>>>

\subsection{RTT measurement}
Regarding the delivery performance, a metric to take in account is the \emph{round trip time}(RTT), that is the time interval between the instant in whic a packet is sent and the response is received. To test it there was developed a script that sends a packet with 8B of payload and waits for the corrispondant response, recording the instants (expressed as \emph{epoch}) of send and receive. The sake of thi test is to compare the RTT measured without any SFC (only sending the packet to the receiver waiting for the response) and making packets pass through different length SFCs, in particular with 1, 2, 3, 4, 5, and 10 hops. Packets traverse the SFC on both sides and the results are collected after 100 tests and the SF only prints the packet received and the total number of packets that have passed throught it.

@@

\begin{figure}[H]
  %\centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[scale=0.4]{meanrtt}
        \caption{Mean RTT calculate using SFCs of different lengths}
        \label{chap:tests:sec:rtt:img:meanstt}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[scale=0.4]{differencenosfc}
        \caption{Time increase using SFCs of different lengths}
        \label{chap:tests:sec:rtt:img:differencertt}
    \end{subfigure}
\end{figure}

The results are better represented in Figure~\ref{chap:tests:sec:rtt:img:meanstt}. In that graph we can easier see the difference among the chains with different lengths and the trasmission that does not use any SFC. Looking at the bars representing the SFC composed by 1, 2, 3, 4 and 5 links we can see a pretty linear increase of the RTT. This trend strongly depends on the nature of the SF involved in the SFC, in that case the linear increase is highligted due to the use of the same funcion. In Figure~\ref{chap:tests:sec:rtt:img:differencertt} is depicted the difference between the RTT measured with a normal packet transmission and using the chains with different size, that represent the additional time needed for each transmission. Even in that case we can see that some time is waisted against a normal transmission and that this delta of time depends on the number of SFC involved in the chain.

\begin{figure}
  \centering
  \includegraphics[scale=0.4]{differenceonehop}
  \caption{Time difference between SFCs that have a length difference of one SF}
  \label{chap:tests:sec:rtt:img:differenceonehop}
\end{figure}

In Figure~\ref{chap:tests:sec:rtt:img:differenceonehop} is represented the difference in terms of RTT among chains that have a length difference of one link. The first bar represent the comparison between an SFC composed by only one element and the direct trasmission to the receiver: that explain why that value is higher than the others. Other differences among SFC, instead, are quite similar.

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
\centering
\begin{tabular}{@{}cc@{}}
\toprule
\textbf{SFC length} & \textbf{Jitter (Milliseconds)} \\ \midrule
len. 0              & 0.0001074767    \\
len. 1              & 0.0028695822    \\
len. 2              & 0.0032037902    \\
len. 3              & 0.0031961584    \\
len. 4              & 0.0027278513    \\
len. 5              & 0.0036802184    \\
len. 10             & 0.0063434506    \\ \bottomrule
\end{tabular}
\caption{Jitterf for different SFC lengths}
\label{chap:tests:sec:rtt:tab:jitter}
\end{table}

Table~\ref{chap:tests:sec:rtt:tab:jitter} represent the jitter calculated for different SFC length, based on values of RTT measured in the previous test. Jitter is the variation in the delay of received packet, and gives a measure of the congestion of the network. As we can see values are really low, even if the lowest one is always the one calculated without the chain.
